### 2020-04-03 paper/sections/design.tex
change to TOMM template

\begin{figure*}[!t]
	%\begin{tabular}{cc}
	\begin{minipage}{\linewidth}
		\centerline{\includegraphics[width=0.8\linewidth]{figures/conventional-framework.pdf}}
		\begin{center}
			{(a) Conventional solution: fixed user-defined compression quality level}
		\end{center}
		%        \vspace{0.3cm}
	\end{minipage}
	\vfill
	\vspace{0.4cm}
	\begin{minipage}{\linewidth}
		\centerline{\includegraphics[width=0.8\linewidth]{figures/adaptive-framework.pdf}}
		\vspace{0.2cm}
		\begin{center}
			{(b) AdaCompress solution: input image and model aware compression}
		\end{center}
	\end{minipage}
	%\end{tabular}
	\vspace{0.1cm}
	\caption{Comparing to the conventional solution, our solution can update the compression strategy based on the backend model feedback}
	\label{fig: framework}
\end{figure*}

@@

\begin{figure*}[!t]
	\centerline{\includegraphics[width=0.8\linewidth]{figures/overall-diagram.pdf}}
	\vspace{0.2cm}
	\caption{Diagram of AdaCompress architecture}
	\label{fig: diagram}
\end{figure*}

@@

%\subsubsection{\textbf{Inference}}
\subsubsection{Inference}

@@

%\subsubsection{\textbf{Estimation}}
\subsubsection{Estimation}

@@

%\subsubsection{\textbf{Model Querying}}
\subsubsection{Model Querying}

@@

%\subsubsection{\textbf{Re-training}}
\subsubsection{Re-training}

@@

%\subsubsection{\textbf{Compression Level Choice Variation}}
\subsubsection{Compression Quality Level Choice Variation}

@@

\begin{figure}[!t]
	\includegraphics[width=\linewidth]{figures/quality_chosen.pdf}
	\caption{Histogram of RL agent's best compression quality level selection for different cloud services}
	\label{fig: quality_chosen}
	% \vspace{-0.3cm}
\end{figure}

@@

%\begin{figure}[H]
%    \includegraphics[width=\linewidth]{figures/dataset_change.pdf}
%    \caption{Histogram of RL agent's best compression level selection for different scenery image inputs}
%    \label{fig: dataset_change}
%\end{figure}

\begin{figure}[!t]
	\includegraphics[width=\linewidth]{figures/dataset_change.pdf}
	\caption{Histogram of RL agent's best compression quality level selection for different input image ``sceneries''}
	\label{fig: dataset_change}
\end{figure}

%\subsubsection{\textbf{Attention Map Variation}}
\subsubsection{Attention Map Variation}
\label{subsec: attention map}

@@

\begin{figure*}[!t]
	\begin{minipage}{0.2\linewidth}
		\centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/robust_figure1.png}}
		\centerline{(1a) Q=5}
	\end{minipage}
	\hfill
	\begin{minipage}{0.2\linewidth}
		\centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/robust_figure2.png}}
		\centerline{(1b) Q=15}
	\end{minipage}
	\hfill
	\begin{minipage}{0.2\linewidth}
		\centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/robust_figure3.png}}
		\centerline{(1c) Q=15}
	\end{minipage}
	\hfill
	\begin{minipage}{0.2\linewidth}
		\centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/robust_figure4.png}}
		\centerline{(1d) Q=15}
	\end{minipage}

@@

	\begin{minipage}{0.2\linewidth}
		\centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/sensetive_figure1.png}}
		\centerline{(2a) Q=85}
	\end{minipage}
	\hfill
	\begin{minipage}{0.2\linewidth}
		\centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/sensetive_figure2.png}}
		\centerline{(2b) Q=85}
	\end{minipage}
	\hfill
	\begin{minipage}{0.2\linewidth}
		\centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/sensetive_figure3.png}}
		\centerline{(2c) Q=75}
	\end{minipage}
	\hfill
	\begin{minipage}{0.2\linewidth}
		\centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/sensetive_figure4.png}}
		\centerline{(2d) Q=75}
	\end{minipage}
	\vspace{0.2cm}
	\caption{Visualization of the importance map for the RL agent to choose a compression quality level}
	\label{fig: attention}
\end{figure*}

>>>>

\begin{figure*}[!t]
	%\begin{tabular}{cc}
	\begin{minipage}{\linewidth}
		\centerline{\includegraphics[width=0.8\linewidth]{figures/conventional-framework.pdf}}
		\begin{center}
			{(a) Conventional solution: fixed user-defined compression quality level}
		\end{center}
		%        \vspace{0.3cm}
	\end{minipage}
	\vfill
	\vspace{0.4cm}
	\begin{minipage}{\linewidth}
		\centerline{\includegraphics[width=0.8\linewidth]{figures/adaptive-framework.pdf}}
		\vspace{0.2cm}
		\begin{center}
			{(b) AdaCompress solution: input image and model aware compression}
		\end{center}
	\end{minipage}
	%\end{tabular}
	%\vspace{0.1cm}
	\caption{Comparing to the conventional solution, our solution can update the compression strategy based on the backend model feedback}
	\label{fig: framework}
\end{figure*}

@@

\begin{figure}[!t]
	\centerline{\includegraphics[width=0.8\linewidth]{figures/overall-diagram.pdf}}
%	\vspace{0.2cm}
	\caption{Diagram of AdaCompress architecture}
	\label{fig: diagram}
\end{figure}

%\begin{figure}[H]
%	\centerline{\includegraphics[width=0.8\linewidth]{figures/overall-diagram.pdf}}
%	\vspace{0.2cm}
%	\caption{Diagram of AdaCompress architecture}
%	\label{fig: diagram}
%\end{figure}

@@

%\subsubsection{\textbf{Inference}}
\subsubsection{Inference:}

@@

%\subsubsection{\textbf{Estimation}}
\subsubsection{Estimation:}

@@

%\subsubsection{\textbf{Model Querying}}
\subsubsection{Model Querying:}

@@

%\subsubsection{\textbf{Re-training}}
\subsubsection{Re-training:}

@@

%\subsubsection{\textbf{Compression Level Choice Variation}}
\subsubsection{Compression Quality Level Choice Variation:}

@@

\begin{figure}[!t]
	\includegraphics[width=0.8\linewidth]{figures/quality_chosen.pdf}
	\caption{Histogram of RL agent's best compression quality level selection for different cloud services}
	\label{fig: quality_chosen}
	% \vspace{-0.3cm}
\end{figure}

@@

\begin{figure}[!t]
    \includegraphics[width=0.8\linewidth]{figures/dataset_change.pdf}
    \caption{Histogram of RL agent's best compression level selection for different scenery image inputs}
    \label{fig: dataset_change}
\end{figure}

%\begin{figure}[!t]
%	\includegraphics[width=\linewidth]{figures/dataset_change.pdf}
%	\caption{Histogram of RL agent's best compression quality level selection for different input image ``sceneries''}
%	\label{fig: dataset_change}
%\end{figure}

%\subsubsection{\textbf{Attention Map Variation}}
\subsubsection{Attention Map Variation:}
\label{subsec: attention map}

@@

\begin{figure*}[!t]
	\begin{minipage}{0.2\linewidth}
		\centerline{\includegraphics[width=3.5cm, height=3.0cm]{figures/robust_figure1.png}}
		\centerline{(1a) Q=5}
	\end{minipage}
	\hfill
	\begin{minipage}{0.2\linewidth}
		\centerline{\includegraphics[width=3.5cm, height=3.0cm]{figures/robust_figure2.png}}
		\centerline{(1b) Q=15}
	\end{minipage}
	\hfill
	\begin{minipage}{0.2\linewidth}
		\centerline{\includegraphics[width=3.5cm, height=3.0cm]{figures/robust_figure3.png}}
		\centerline{(1c) Q=15}
	\end{minipage}
	\hfill
	\begin{minipage}{0.2\linewidth}
		\centerline{\includegraphics[width=3.5cm, height=3.0cm]{figures/robust_figure4.png}}
		\centerline{(1d) Q=15}
	\end{minipage}

@@

	\begin{minipage}{0.2\linewidth}
		\centerline{\includegraphics[width=3.5cm, height=3.0cm]{figures/sensetive_figure1.png}}
		\centerline{(2a) Q=85}
	\end{minipage}
	\hfill
	\begin{minipage}{0.2\linewidth}
		\centerline{\includegraphics[width=3.5cm, height=3.0cm]{figures/sensetive_figure2.png}}
		\centerline{(2b) Q=85}
	\end{minipage}
	\hfill
	\begin{minipage}{0.2\linewidth}
		\centerline{\includegraphics[width=3.5cm, height=3.0cm]{figures/sensetive_figure3.png}}
		\centerline{(2c) Q=75}
	\end{minipage}
	\hfill
	\begin{minipage}{0.2\linewidth}
		\centerline{\includegraphics[width=3.5cm, height=3.0cm]{figures/sensetive_figure4.png}}
		\centerline{(2d) Q=75}
	\end{minipage}
%	\vspace{0.2cm}
	\caption{Visualization of the importance map for the RL agent to choose a compression quality level}
	\label{fig: attention}
\end{figure*}

### 2020-04-03 paper/sections/evaluation.tex
minor
change to TOMM template

\begin{table}[htbp]
	\centering
	%     \begin{tabular}{llllll}
	\begin{tabular}{cccccc}
		\toprule
		notation          & value & & & notation     & value  \\ \midrule
		$c_{\rm ref}$ & 75    & & & $K$      & 1000   \\
		$\epsilon_{\min}$    & 0.02  & & & $p_0$    & 0.2    \\
		$\gamma$      & 0.95  & & & $\omega$ & -3   \\
		$ \mu_{\rm dec} $ & 0.99 & & & $ T $ & 5  \\
		$r_{\rm th}$  & 0.45   & & &   $ n  $  &  10      \\ \bottomrule
	\end{tabular}
	\caption{Experiment parameter}
	\label{tab: parameters}
	\vspace{-0.5cm}
\end{table}

@@

The default compression quality level for JPEG is usually 75~\cite{pillow_benchmark,imgmin}. Therefore we regard this as a reference value $ c_{\rm ref} = 75 $ of the conventional benchmark. %% \\

@@

\begin{figure}[htbp]
	\includegraphics[width=\linewidth]{figures/train_steps_new.pdf}
	\caption{Size overhead in the training and inference phase}
	\label{fig: train_steps}
	% \vspace{-0.3cm}
\end{figure}

@@

\begin{figure}[htbp]
	\includegraphics[width=\linewidth]{figures/compress-performance.pdf}
	\caption{Average size and relative accuracy on different cloud services}
	\label{fig: compress_performance}
	% \vspace{-0.3cm}
\end{figure}

@@

\begin{figure}[htbp]
	\includegraphics[width=\linewidth]{figures/compare_DeepN.pdf}
	\caption{Comparative compression performance between DeepN-JPEG and AdaCompress}
	\label{fig: compare_DeepN}
	%    \vspace{-0.3cm}
\end{figure}

@@

\begin{figure*}[htbp]
	\begin{minipage}{0.3\linewidth}
		\centerline{\includegraphics[width=4.0cm,trim=0 80 0 100,clip ]{figures/parrot_q75.jpeg}}
		\centerline{(1a) Origin Image (Q=75)}
		\centerline{Baidu prediction \ = \ [``parrot'']}
	\end{minipage}
	\hfill
	\begin{minipage}{0.2\linewidth}
		\centerline{\includegraphics[width=4.0cm,trim=0 80 0 100,clip ]{figures/parrot_q15.jpeg}}
		\centerline{(1b) AdaCompress (choose Q=15)}
		\centerline{Baidu prediction \ = \ [``parrot'']}
	\end{minipage}
	\hfill
	\begin{minipage}{0.3\linewidth}
		\centerline{\includegraphics[width=4.0cm,trim=0 80 0 100,clip ]{figures/parrot_deepn.jpeg}}
		\centerline{(1c) DeepN-JPEG}
		\centerline{Baidu prediction \ = \ [``parrot'']}
	\end{minipage}

@@

%\begin{figure}[htbp]
%    \includegraphics[width=\linewidth]{figures/running-retrain.pdf}
%    \caption{AdaCompress's reaction upon scenery change}
%%    \vspace{-0.2cm}
%    \label{fig: running-retrain}
%\end{figure}
\begin{figure}[H]
	\includegraphics[width=\linewidth]{figures/running-retrain.pdf}
	\caption{AdaCompress's reactions upon scenery change}
	%    \vspace{-0.2cm}
	\label{fig: running-retrain}
\end{figure}

@@

\begin{table}[htbp]
	% \begin{table}[H]
	\centering
	%     \begin{tabular}{lll}
	\begin{tabular}{ccc}
		\toprule
		& Benchmark & AdaCompress  \\ \midrule
		Average upload size          & 42.68 KB  &  18.46 KB            \\
		Inference latency    & 0 s       & 2.09 ms          \\
		Transmission latency & 12.35 ms       & 5.34 ms          \\
		Overall latency      & 12.35 ms       & 7.43 ms          \\ \bottomrule
	\end{tabular}
	\caption{Latency between image upload and inference result feedback}
	\label{tab: latency-overhead}
	% \vspace{-0.5cm}
\end{table}

>>>>

\begin{table*}[!t]
	\centering
	\caption{Experiment parameter}
	\label{tab: parameters}
	%     \begin{tabular}{llllll}
	\begin{tabular}{cccccc}
		\toprule
		notation          & value & & & notation     & value  \\ \midrule
		$c_{\rm ref}$ & 75    & & & $K$      & 1000   \\
		$\epsilon_{\min}$    & 0.02  & & & $p_0$    & 0.2    \\
		$\gamma$      & 0.95  & & & $\omega$ & -3   \\
		$ \mu_{\rm dec} $ & 0.99 & & & $ T $ & 5  \\
		$r_{\rm th}$  & 0.45   & & &   $ n  $  &  10      \\ \bottomrule
	\end{tabular}
%	\vspace{-0.5cm}
\end{table*}

@@

The default compression quality level for JPEG is usually $75$ \cite{pillow_benchmark,imgmin}. Therefore we regard this as a reference value $ c_{\rm ref} = 75 $ of the conventional benchmark.

@@

\begin{figure}[!t]
	\includegraphics[width=0.8\linewidth]{figures/train_steps_new.pdf}
	\caption{Size overhead in the training and inference phase}
	\label{fig: train_steps}
	% \vspace{-0.3cm}
\end{figure}

@@

\begin{figure}[!t]
	\includegraphics[width=0.8\linewidth]{figures/compress-performance.pdf}
	\caption{Average size and relative accuracy on different cloud services}
	\label{fig: compress_performance}
	% \vspace{-0.3cm}
\end{figure}

@@

\begin{figure}[!t]
	\includegraphics[width=0.8\linewidth]{figures/compare_DeepN.pdf}
	\caption{Comparative compression performance between DeepN-JPEG and AdaCompress}
	\label{fig: compare_DeepN}
	%    \vspace{-0.3cm}
\end{figure}

@@

\begin{figure*}[!t]
	\begin{minipage}{0.3\linewidth}
		\centerline{\includegraphics[width=4.0cm,trim=0 80 0 100,clip ]{figures/parrot_q75.jpeg}}
		\centerline{(1a) Origin Image (Q=75)}
		\centerline{Baidu prediction \ = \ [``parrot'']}
	\end{minipage}
	\hfill
	\begin{minipage}{0.2\linewidth}
		\centerline{\includegraphics[width=4.0cm,trim=0 80 0 100,clip ]{figures/parrot_q15.jpeg}}
		\centerline{(1b) AdaCompress (choose Q=15)}
		\centerline{Baidu prediction \ = \ [``parrot'']}
	\end{minipage}
	\hfill
	\begin{minipage}{0.3\linewidth}
		\centerline{\includegraphics[width=4.0cm,trim=0 80 0 100,clip ]{figures/parrot_deepn.jpeg}}
		\centerline{(1c) DeepN-JPEG}
		\centerline{Baidu prediction \ = \ [``parrot'']}
	\end{minipage}

@@

%\begin{figure}[!t]
%    \includegraphics[width=\linewidth]{figures/running-retrain.pdf}
%    \caption{AdaCompress's reaction upon scenery change}
%%    \vspace{-0.2cm}
%    \label{fig: running-retrain}
%\end{figure}
\begin{figure}[!t]
	\includegraphics[width=0.8\linewidth]{figures/running-retrain.pdf}
	\caption{AdaCompress's reactions upon scenery change}
	%    \vspace{-0.2cm}
	\label{fig: running-retrain}
\end{figure}

@@

\begin{table*}[!t]
	\centering
	\caption{Latency between image upload and inference result feedback}
	\label{tab: latency-overhead}
	%     \begin{tabular}{lll}
	\begin{tabular}{ccc}
		\toprule
		& Benchmark & AdaCompress  \\ \midrule
		Average upload size          & 42.68 KB  &  18.46 KB            \\
		Inference latency    & 0 s       & 2.09 ms          \\
		Transmission latency & 12.35 ms       & 5.34 ms          \\
		Overall latency      & 12.35 ms       & 7.43 ms          \\ \bottomrule
	\end{tabular}
	% \vspace{-0.5cm}
\end{table*}

### 2020-04-03 paper/sections/introduction.tex
change to TOMM template

\IEEEPARstart{W}{ith} the great success of deep learning in computer vision, this decade has witnessed an explosion of deep learning-based computer vision-based applications. Because of the enormous computational resource consumption for deep learning applications (e.g., inferring an image on VGG19~\cite{VGG19} requires $20$ GFLOPs of GPU resource), in today's online computer vision-based applications, users usually have to upload the input images to the central cloud service providers (e.g., SenseTime, Baidu Vision and Google Vision, etc.), leading to a significant upload traffic load.

@@

\begin{figure*}[!t]
%	\begin{tabular}{cc}
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 150 0 150, clip]{figures/donut_q75.jpeg}}
		\centerline{(1a) Q=75}
%		\centerline{Face++ prediction=["donut"]}
		\centerline{Face++ prediction \ = \ [``donut'']}
		\vspace{0.4cm}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 150 0 150, clip]{figures/donut_q55.jpeg}}
		\centerline{(1b) Q=55}
%		\centerline{Face++ prediction=[]}
		\centerline{Face++ prediction \ = \ [``biscuit'']}
		\vspace{0.4cm}
	\end{minipage}
	\vfill	
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 0 0 0]{figures/chameleon_q75.jpeg}}
		\centerline{(2a) Q=75}
% 		\centerline{\quad Baidu prediction=["chameleon"]}
		\centerline{Baidu prediction \ = \ [``chameleon'']}
		\vspace{0.4cm}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 0 0 0]{figures/chameleon_q55.jpeg}}
		\centerline{(2b) Q=55}
% 		\centerline{\qquad Baidu prediction=["electric fan"]}
 		\centerline{Baidu prediction \ = \ [``electric fan'']}
 		\vspace{0.4cm}
	\end{minipage}
	\vfill
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 0 0 0, clip]{figures/tiger_highq.jpeg}}
		\centerline{(3a) Q=75}
%		\centerline{Baidu prediction=["leopard"]}
		\centerline{Baidu prediction \ = \ [``leopard'']}
		\vspace{0.3cm}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 0 0 0, clip]{figures/tiger_lowq.jpeg}}
		\centerline{(3b) Q=5}
%		\centerline{Baidu prediction=["leopard"]}
		\centerline{Baidu prediction \ = \ [``leopard'']}
		\vspace{0.3cm}
	\end{minipage}
%	\end{tabular}
	\caption{The prediction of a deep learning model is not completely related to the input image's quality, making it difficult to use a fixed compression quality for all images. For image 1a, 1b and 2a, 2b, minor changes cause different predictions though they are visually similar; for image 3a and 3b, the cloud-based model still output correct label from a severely compressed image though they look very different}
	\label{fig: compress_accuracy}
%	\vspace{-0.1cm}
\end{figure*}

>>>>

With the great success of deep learning in computer vision, this decade has witnessed an explosion of deep learning-based computer vision-based applications. Because of the enormous computational resource consumption for deep learning applications (e.g., inferring an image on VGG19~\cite{VGG19} requires $20$ GFLOPs of GPU resource), in today's online computer vision-based applications, users usually have to upload the input images to the central cloud service providers (e.g., SenseTime, Baidu Vision and Google Vision, etc.), leading to a significant upload traffic load.

@@

\begin{figure*}[!t]
%	\begin{tabular}{cc}
	\begin{minipage}{0.4\linewidth}
		\centerline{\includegraphics[width=4.5cm, trim=0 150 0 150, clip]{figures/donut_q75.jpeg}}
		\centerline{(1a) Q=75}
%		\centerline{Face++ prediction=["donut"]}
		\centerline{Face++ prediction \ = \ [``donut'']}
		\vspace{0.4cm}
	\end{minipage}
	\hfill
	\begin{minipage}{0.4\linewidth}
		\centerline{\includegraphics[width=4.5cm, trim=0 150 0 150, clip]{figures/donut_q55.jpeg}}
		\centerline{(1b) Q=55}
%		\centerline{Face++ prediction=[]}
		\centerline{Face++ prediction \ = \ [``biscuit'']}
		\vspace{0.4cm}
	\end{minipage}
	\vfill	
	\begin{minipage}{0.4\linewidth}
		\centerline{\includegraphics[width=4.5cm, trim=0 0 0 0]{figures/chameleon_q75.jpeg}}
		\centerline{(2a) Q=75}
% 		\centerline{\quad Baidu prediction=["chameleon"]}
		\centerline{Baidu prediction \ = \ [``chameleon'']}
		\vspace{0.4cm}
	\end{minipage}
	\hfill
	\begin{minipage}{0.4\linewidth}
		\centerline{\includegraphics[width=4.5cm, trim=0 0 0 0]{figures/chameleon_q55.jpeg}}
		\centerline{(2b) Q=55}
% 		\centerline{\qquad Baidu prediction=["electric fan"]}
 		\centerline{Baidu prediction \ = \ [``electric fan'']}
 		\vspace{0.4cm}
	\end{minipage}
	\vfill
	\begin{minipage}{0.4\linewidth}
		\centerline{\includegraphics[width=4.5cm, trim=0 0 0 0, clip]{figures/tiger_highq.jpeg}}
		\centerline{(3a) Q=75}
%		\centerline{Baidu prediction=["leopard"]}
		\centerline{Baidu prediction \ = \ [``leopard'']}
		\vspace{0.4cm}
	\end{minipage}
	\hfill
	\begin{minipage}{0.4\linewidth}
		\centerline{\includegraphics[width=4.5cm, trim=0 0 0 0, clip]{figures/tiger_lowq.jpeg}}
		\centerline{(3b) Q=5}
%		\centerline{Baidu prediction=["leopard"]}
		\centerline{Baidu prediction \ = \ [``leopard'']}
%		\vspace{0.4cm}
	\end{minipage}
%	\end{tabular}
	\caption{The prediction of a deep learning model is not completely related to the input image's quality, making it difficult to use a fixed compression quality for all images. For image 1a, 1b and 2a, 2b, minor changes cause different predictions though they are visually similar; for image 3a and 3b, the cloud-based model still output correct label from a severely compressed image though they look very different}
	\label{fig: compress_accuracy}
%	\vspace{-0.1cm}
\end{figure*}
